Stack Safety as a Security Property

### 2020-06-13 main.tex
Updated WBCF in tex and coq

  \definition{Well-bracketed Control Flow}

    Well-bracketed control flow captures the expected behavior of marked
    returns with regard to their call points. The coinductive {\em bracketing}
    predicate, \(\mathit{BR}(\machT)\), is parameterized by a call map
    \(\callmap\) and a return map \(\retmap\):

    \[\frac{\mathit{BR}(\machT) \hspace{.5cm} \callmap(\mach_c(\PCname)) = n
              \hspace{.5cm} \retmap(\mach_c(\PCname))}
           {\mathit{BR}(\mach_c \machT \mach_r)}\]

    \[\frac{\mathit{BR}(\machT) \hspace{.5cm} \callmap(\mach(\PCname)) = \bot}
           {\mathit{BR}(\mach \machT)}\]

    A system enjoys {\em well-bracketed control flow} with regard to a call map
    \(\callmap\) and return map \(\retmap\) if for any initial state
    \(\mach_0\) and any call state and policy state \(\mach_c\) and \(\pol_c\)
    in the induced trace from \(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
    \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT \mpostate{\mach'}
    {\pol'}{\obs'} ...\) and \(\MPT\) is bracketed with regard to \(\callmap\)
    and \(\retmap\), then \(\ret{\mach_c,\mach'}\).

  \definition{Standard Stack Control Flow}

    The above properties are somewhat orthogonal, but together they capture a
    standard notion of control flow for a stack: functions keep their code
    separate outside of calls and returns, calls respect explicit entry points,
    and returns respect implicit entry points corresponding to their call.
    A system that enjoys them with regard to a code, a call, a return, and an
    entry map is said to enjoy {\em standard stack control flow} with regard to
    those maps.

>>>>

  \definition{Return Integrity}

    Return integrity captures the expected behavior of marked returns with
    regard to their call points. We begin by defining a coinductive relation
    \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_1 \MPT_2\). Given a call map
    \(\callmap\) and return map \(\retmap\), \(\MPT\) is related to
    \(\MPT'\) if \(\MPT'\) is a suffix of \(\MPT\) whose head is the first
    unmatched return in \(\MPT\). So if \(\MPT\) starts with a return,
    it is related to itself:
%
    \[\frac{\callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \retmap(\mach(\PCname))}
           {\mathit{Unmatched}\ \callmap\ \retmap\ \mpstate{\mach}{\pol}\ 
              \mpstate{\mach}{\pol}}\]
    \[\frac{\callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \retmap(\mach(\PCname))}
           {\mathit{Unmatched}\ \callmap\ \retmap\ \mpstate{\mach}{\pol}\MPT\ 
              \mpstate{\mach}{\pol}\MPT}\]
%
    If \(\MPT\) starts with a non-call, non-return state, its unmatched
    return must come later:
%
    \[\frac{\begin{split}
            & \callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \neg \retmap(\mach(\PCname)) \\
            & \mathit{Unmatched}\ \callmap\ \retmap\ \MPT\ \MPT'
            \end{split}}
           {\mathit{Unmatched}\ \callmap\ \retmap\ 
            \mpstate{\mach}{\pol}\MPT\ \MPT'}\]
%   
    And most intricately, if \(\MPT\) starts with a call, we must find the
    return that matches it, which will be the unmatched return once we step
    past the call. Then the first unmatched return beyond it is the true
    unmatched return.
    \[\frac{\begin{split}
            & \callmap(\mach(\PCname)) = n
              \hspace{.5cm} \neg \retmap(\mach(\PCname)) \\
            & \MPT = \mpstate{\mach}{\pol} \MPT_{\mathit{call}} \\
            & \mathit{Unmatched}\ \callmap\ \retmap\ \MPT_{\mathit{call}}\ \MPT_{\mathit{matched}} \\
            & \MPT_{\mathit{matched}} = \mpstate{\mach'}{\pol'} \MPT_{\mathit{tail}} \\
            & \mathit{Unmatched}\ \callmap\ \retmap\ \MPT_{\mathit{tail}}\ \MPT_{\mathit{unmatched}} \\
            \end{split}}
            {\mathit{Unmatched}\ \callmap\ \retmap\ \MPT\ \MPT_{\mathit{unmatched}}}\]

    A system enjoys {\em return integrity} with regard to a call map
    \(\callmap\) and return map \(\retmap\) if for any initial state
    \(\mach_0\) and any call state and policy state \(\mach_c\) and \(\pol_c\)
    in the induced trace from \(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
    \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT\) and \(\mach_r\) is the
    first unmatched return, with \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT
    \ \MPT'\) and \(\mach_r\) the first machine state of \(\MPT'\),
    then \(\ret{\mach_c}\ \mach_r\).

  \definition{Well Bracketed Control Flow}

    The above properties are somewhat orthogonal, but together they capture a
    standard notion of control flow for a stack: functions keep their code
    separate outside of calls and returns, calls respect explicit entry points,
    and returns respect implicit entry points corresponding to their call.
    A system that enjoys them with regard to a code, a call, a return, and an
    entry map is said to enjoy {\em well bracketed control flow} with regard to
    those maps.
